\documentclass[10pt]{article}
\usepackage[margin=0.55in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=*, topsep=1pt, itemsep=1pt, parsep=0pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{3pt}

\begin{document}

\begin{center}
{\LARGE Example Candidate}\\
\href{mailto:example.candidate@example.com}{example.candidate@example.com} \textbar{}
555-010-1234 \textbar{}
\href{https://example.com}{example.com} \textbar{}
\href{https://github.com/example-candidate}{github.com/example-candidate}
\end{center}

\section*{Summary}
Full-stack product engineer with 5 years of experience building React, TypeScript, and Node.js features for workflow-heavy SaaS products. Strong in customer-facing UI, API integration, performance improvements, and cross-functional delivery with product and design partners.

\section*{Skills}
\textbf{Languages:} TypeScript, JavaScript, SQL \\
\textbf{Frontend:} React, HTML, CSS, accessibility basics \\
\textbf{Backend:} Node.js, REST APIs, PostgreSQL, MongoDB basics \\
\textbf{Testing/Tools:} Jest, integration tests, Git, CI, documentation

\section*{Experience}
\textbf{ExampleCo Labs} \hfill Remote \\
\textit{Software Engineer} \hfill 2021--Present
\begin{itemize}
  \item Built React and TypeScript workflow configuration screens for a B2B SaaS product, improving setup clarity across multi-step customer flows.
  \item Developed Node.js REST endpoints for workflow state, validation, and save operations used by customer-facing product surfaces.
  \item Improved dashboard filtering performance by reducing unnecessary requests and rendering work in dense table views.
  \item Added integration tests and API documentation for shared workflow endpoints, making failure cases easier for the team to diagnose.
\end{itemize}

\textbf{Sample Systems} \hfill Remote \\
\textit{Associate Software Engineer} \hfill 2019--2021
\begin{itemize}
  \item Built internal operations tools used by support and account teams to review customer status, notes, and follow-up tasks.
  \item Automated recurring data cleanup tasks with SQL and Node.js scripts, reducing manual spreadsheet updates.
\end{itemize}

\section*{Projects}
\textbf{Task Queue Demo} \hfill TypeScript, Node.js, PostgreSQL, React
\begin{itemize}
  \item Built a small app to normalize tasks, statuses, owners, and due dates with duplicate detection.
\end{itemize}

\textbf{Metrics Viewer Demo} \hfill React, TypeScript, PostgreSQL
\begin{itemize}
  \item Built dashboard views for activity counts, item trends, and conversion-style summaries using filterable charts.
\end{itemize}

\section*{Education}
\textbf{State University} \hfill B.S. Computer Science

\end{document}
